Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-06 Cover_letter_JPM.tex
Updates from Overleaf

\begin{MyColorPar}{blue}
Answer\\
%(OK)
We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

@@

\begin{MyColorPar}{blue}
Answer\\
%(OK)
After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript.

@@

Since the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P} = 0.05),
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
we reviewed the results of cutoffs from 50\% to 70\% quantile to find the evidence.
%> View(hazards[hazards$Gene.Symbol %in% c(gene_labeled_silver, gene_labeled_golden), c("Gene.Symbol","FDR.Pvalue")])
A total of 20 preliminary candidates have FDR-corrected \textit{P} values from \num{3.78e-6} to \num{3.03e-4} (please see Table \ref{table:table1} and \ref{table:table3}; also shown in supplementary Table S1, S2).
The top 3 biomarker candidates, CAMK2N1, CALML5, and FCGBP, have FDR-corrected \textit{P} values from \num{1.63e-5} to \num{1.97e-4} (please see Figure \ref{fig:figure4}, 
%which have been grouped by cutoffs between; 
it is also shown in manuscript as updated "Figure 5").
Moreover, the gene NDFIP1, one of the 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff.
NDFIP1 also has a \textit{P} value of \num{2.62e-6} when cut at 70\% quantile  (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure S1). 
After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to determine its effect size (hazard ratio) then to be validated by the other independent cohort.

@@

\resizebox{0.6\linewidth}{!}{%

@@

\begin{tabularx}{\textwidth}{|l|p{6.0cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}

@@

\clearpage

@@

% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title, "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

@@

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
%
% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort, CAMK2N1, CALML5, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the biomarker.
%In the consensus of TCGA and GSE65858 cohorts,

@@

We modified the paragraphs in the "Materials and Methods" section, and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
% ok
The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 567 to line 580),
% results ok
the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 154) to page 6 (line 169) , and
% ok
the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 233) to page 11 (line 284)
are the part of the manuscript that has been revised. 
Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

\textcolor{blue}{In the section of Results}\\
"
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure 2(c), (d)).
%em dash ---
These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, EVPLL, PNMA5, IQCN, NPB, and CALML5) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

We appreciate the reviewer for the critical comments.
Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
%Least Absolute Shrinkage and Selection Operation (LASSO):
Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e. twenty thousands of features (genes) and only hundreds of sample size.
The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
Our approach is to build a logistic regression model for the prediction of patient's survival.
% over-fitting causes problem
% During fitting of logistic model, 
Beside feature selection,
it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
$\lambda$ could control the amount of bias dealing with over-fitting.
%(over-fitting is called high-variance)
In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
% perhaps the simplest and 
Cross-validation error is calculated to find the optimal value of $\lambda$.
%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
% k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
the important features that contribute much to the model will be selected under that optimal value of $\lambda$.

% multinomial
%RLassoCox\\
We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient. 
% RLassoCox includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
% gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
The model training has been performed under 10-fold cross-validation.
% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
%#Calculating Cox p-value...Done [2021/06/22] 19:42
%#Performing directed random walk...Done
%#Performing cv.glmnet...Done
%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
%cv.mod.candidate has 62 genes 
The results shows the selected features (62 genes) distributing on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}).

@@

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
We have further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
According to their \textit{P} values (please see Table \ref{tab:signature4}), 
we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1 in volcano plot of TCGA HNSCC.

@@

\begin{table}[ht]
\centering
\caption{The most LASSO regularized logistic model under cross-validation. Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
    (\textcolor{red}{red}-marked logistic \textit{P} value $< 0.05$)}
\label{tab:signature4}
\begin{tabular}{lrr}
\textbf{Gene Symbol} & \textbf{Coefficients} &  \textbf{\textit{P} value} \\ \hline
\textbf{POLR2C}      & 0.870                 & 0.150                              \\
\textbf{EFNB2}       & 0.189                 & 0.521                              \\
\textbf{PLAU}        & -0.189                & 0.408                              \\
\textbf{HK1}         & 1.413                 & \textcolor{red}{0.002}       \\
\textbf{WNT7A}       & 0.211                 & 0.111                              \\
\textbf{HPRT1}       & 0.620                 & 0.113                              \\
\textbf{APP}         & 0.219                 & 0.538                              \\
\textbf{SC5DL}       & 0.262                 & 0.367                              \\
\textbf{EZR}         & 0.973                 & \textcolor{red}{0.017}       \\
\textbf{RRAGA}       & 0.925                 & \textcolor{red}{0.022}       \\
\textbf{S1PR4}       & -0.368                & 0.052                              \\
\textbf{DUSP16}      & -0.745                & \textcolor{red}{0.035}       \\
\textbf{SH3BP2}      & -0.606                & 0.107                             
\end{tabular}
\end{table}

@@

In conclusion, we might build a Lasso regression model with LASSO regularization to maximize the use of continuous gene expression values (without the need of a cutoff).
The gene signature integrating multiple genes is also a good approach for biomarker discovery.
However, the resulting candidates could be influenced by proper "gene interaction network" applied for model building.
% gene signature
RLassoCox package works on the basis of gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
RLassoCox utilizes Kyoto Encyclopedia of Genes and Genomes (KEGG) network\cite{Simon2011} as the reference of gene interaction networks, constructed by the R package "iSubpathwayMiner".
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.

>>>>

\begin{MyColorPar}{blue}
Answer\\
%(OK)

We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

@@

\begin{MyColorPar}{blue}
Answer\\
%(OK)

After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript.

@@

Since the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P} = 0.05),
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
we reviewed the results of cutoffs from 50\% to 70\% quantile to find the evidence.
%> View(hazards[hazards$Gene.Symbol %in% c(gene_labeled_silver, gene_labeled_golden), c("Gene.Symbol","FDR.Pvalue")])
A total of 20 preliminary candidates have FDR-corrected \textit{P} values from \num{3.78e-6} to \num{3.03e-4} (please see Table \ref{table:table1} and \ref{table:table3}; also shown in supplementary Table S1, S2).
The top 3 biomarker candidates, CAMK2N1, CALML5, and FCGBP, have FDR-corrected \textit{P} values from \num{1.63e-5} to \num{1.97e-4} (please see Figure \ref{fig:figure4}, 
%which have been grouped by cutoffs between; 
it is also shown in manuscript as updated "Figure 5").
Moreover, the gene NDFIP1, one of the 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff.
NDFIP1 also has a \textit{P} value of \num{2.62e-6} when cut at 70\% quantile  (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure S1). 
After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more candidates (\textit{P} values far less than $0.0003$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to determine its effect size (hazard ratio) then to be validated by the other independent cohort.

@@

\resizebox{0.65\linewidth}{!}{%

@@

\begin{tabularx}{\textwidth}{|l|p{6.5cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}

@@

%\clearpage

@@

% supplementary figure
\begin{figure}[ht]
    \centering
    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: (1) 70\% of \textit{P} values is $< 0.05$; (2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; (3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>= 0.05$.\\
    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
    \label{fig:pvaluePlot_NDFIP1}
\end{figure}

@@

We appreciate the reviewer for the critical comment.
We changed title, "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

@@

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($< \num{3.0e-4}$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
%
% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort, CAMK2N1, CALML5, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the other 17 genes (discovered in TCGA) are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
Thus, there is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the biomarker.
%In the consensus of TCGA and GSE65858 cohorts,

@@

We modified the paragraphs in the "Materials and Methods" section, and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
% ok
The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 567 to line 580),
% results ok
the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 147) to page 6 (line 169) , and
% ok
the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 233) to page 11 (line 284)
are the part of the manuscript that has been revised. 
Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

\textcolor{blue}{In the section of Results}\\
"
TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure 2(c), (d)).
%, under the stringent criteria 
%em dash ---
These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, EVPLL, PNMA5, IQCN, NPB, and CALML5) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

@@

We appreciate the reviewer for the critical comments.
We tried to integrate multiple genes in survival analysis, using a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
%Least Absolute Shrinkage and Selection Operation (LASSO):
Branders and his colleagues\cite{Branders2014} suggested that regularization of regression model should be applied on analysis of the high-dimensional data, e.g., twenty thousands of features (genes) and only hundreds of sample size.
The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
Our approach is to build a logistic regression model for the prediction of patient's survival.
% over-fitting causes problem
% During fitting of logistic model, 
Beside feature selection,
it is also necessary to add that small amount of bias---lambda ($\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
$\lambda$ could control the amount of bias dealing with over-fitting.
%(over-fitting is called high-variance)
In such a case, over-fitted model will only perfectly match every single case, and has higher variability to predict what it never see.
Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
% perhaps the simplest and 
Cross-validation error is calculated to find the optimal value of $\lambda$.
%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
% k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
the important features that contribute much to the model will be selected under that optimal value of $\lambda$.

% multinomial
%RLassoCox\\
We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) to find the gene signature.
%for training both Cox proportional hazard regression and logistic regression models to identify a group of genes that contribute to survival outcome of HNSCC patient. 
% RLassoCox includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
% gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox makes use of both Cox and LASSO logistic regression for gene-expression based survival analysis of HNSCC.
The model training has been performed under 10-fold cross-validation.
% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
%#Calculating Cox p-value...Done [2021/06/22] 19:42
%#Performing directed random walk...Done
%#Performing cv.glmnet...Done
%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
%cv.mod.candidate has 62 genes 
The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.

@@

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
We further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
According to their \textit{P} values (please see Table \ref{tab:signature4}), 
we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1.0 on the volcano plot of TCGA HNSCC.

@@

\begin{table}[ht]
\centering
\caption{The most LASSO regularized logistic model (under cross-validation error within 1 standard deviation of the minimum). Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
    (\textcolor{red}{red}-marked logistic \textit{P} value $< 0.05$)}
\label{tab:signature4}

\resizebox{0.4\linewidth}{!}{%
\begin{tabular}{lrr}
\textbf{Gene Symbol} & \textbf{Coefficients} &  \textbf{\textit{P} value} \\ \hline
\textbf{POLR2C}      & 0.870                 & 0.150                              \\
\textbf{EFNB2}       & 0.189                 & 0.521                              \\
\textbf{PLAU}        & -0.189                & 0.408                              \\
\textbf{HK1}         & 1.413                 & \textcolor{red}{0.002}       \\
\textbf{WNT7A}       & 0.211                 & 0.111                              \\
\textbf{HPRT1}       & 0.620                 & 0.113                              \\
\textbf{APP}         & 0.219                 & 0.538                              \\
\textbf{SC5DL}       & 0.262                 & 0.367                              \\
\textbf{EZR}         & 0.973                 & \textcolor{red}{0.017}       \\
\textbf{RRAGA}       & 0.925                 & \textcolor{red}{0.022}       \\
\textbf{S1PR4}       & -0.368                & 0.052                              \\
\textbf{DUSP16}      & -0.745                & \textcolor{red}{0.035}       \\
\textbf{SH3BP2}      & -0.606                & 0.107                             
\end{tabular}

} % end resizebox
\end{table}

@@

In conclusion, we might build a logistic regression model with LASSO $L_{1}$-regularization to maximize the use of continuous gene expression values (without cutoff).
The gene signature integrating multiple genes is also a good approach for biomarker discovery.
However, the resulting candidates could be influenced by proper "gene interaction network" applied for model building.
% gene signature
RLassoCox package works on the basis of gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
RLassoCox utilizes Kyoto Encyclopedia of Genes and Genomes (KEGG) network\cite{Simon2011} as the reference of gene interaction networks, constructed by the R package "iSubpathwayMiner".
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
